---
title: "Alcohol vs Seat choice"
author: "Chris Gonzalez"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data



## Now add in boxplot

````{r}
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot() +
  labs(title = "Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))
`````
  
  
### get fancy  

```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol, fill = factor(Seat))) +
  geom_boxplot(notch = TRUE, outlier.colour = "red", outlier.shape = 16) +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightyellow")) +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean amount of alcohol in the back people is 9.625. This results shows that the people in the back are drinking about 3 times the amount than the middle row and about 6 times more than the front. There is 32 people in the back seat, 33 in the front seats and 83 people in the middle rows.  

## Inferential Tests



## Conclusions


