---
title: "Alcohol vs Seat choice"
author: "Chris Gonzalez"
date: "Summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```


## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data



## Now add in boxplot

  
  
### get fancy  

```{r}
ggplot(davisdata, aes(x = Seat, y = alcohol, fill = factor(Seat))) +
  geom_boxplot(notch = TRUE, outlier.colour = "red", outlier.shape = 16) +
  scale_fill_manual(values = c("lightblue", "lightgreen", "lightyellow")) +
  labs(title = "Notched Box Plot of Alcohol by Seat") +
  theme(plot.title = element_text(size = 14, hjust = 0.5))

```

Analyzing the box plot there is a visual difference from the back and front seat. There is not much of a difference between the front and middle seat.



## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```
The mean amount of alcohol in the back people is 9.625. This results shows that the people in the back are drinking about 3 times the amount than the middle row and about 6 times more than the front. There is 32 people in the back seat, 33 in the front seats and 83 people in the middle rows.  

## Inferential Tests

```{r}
# Load the necessary library
library(stats)

# Perform ANOVA test
anova_result <- aov(alcohol ~ Seat, data = davisdata)

# Check the ANOVA table
summary(anova_result)

```
With this test there is no significant difference to make a conclusion because the numbers are so low. 


```{r,eval=FALSE}
plot(TukeyHSD(model1))
```
In order to intrepid this plot we need to use the confidence internal from back compared to the other seats. There is difference from the back seat from other two rounds. There is no difference between the front row and middle row. 




```{r}
# Perform Tukey HSD test
tukey_result <- TukeyHSD(anova_result)

# Print the results
print(tukey_result)


```

The front and back have a very low number p adj meaning there is not significant difference with the


## Conclusions

In summary, based on the analysis, it can be concluded that there is a significant difference in alcohol consumption between the back seat and the other seats. However, no significant difference was observed between the front and middle rows in terms of alcohol consumption.






